Spatial Reasoning and Statistical Graphics

### 2014-11-17 Paper/Draft1/TestingVisualAptitude.Rnw
Move new PC chunk up so it's included in the document.
Remove newtext for text that is no longer new

\newtext{Figure \ref{fig:lineup} shows a sample lineup of boxplots; participants would be expected to determine that sub-plot 4 is the most different because the two groups have notably different medians.}

@@

\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13876a225d34-single}
\caption{QQ Plot with guide line.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13877c93dc78-single}
\caption{QQ Plot with acceptance bands.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13878e5c92f-single}
\caption{QQ Plot rotated 45 degrees.}
\end{figure}
\section{Lineup Plot Types} \label{app:plottypes}
We can also compare participants' performance on specific types of lineup plots compared with their scores on the visual aptitude tests, for instance, accuracy on lineups which require mental rotation may be related to performance on the card rotation task.

>>>>

Figure \ref{fig:lineup} shows a sample lineup of boxplots; participants would be expected to determine that sub-plot 4 is the most different because the two groups have notably different medians.

@@

\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13876a225d34-single}
\caption{QQ Plot with guide line.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13877c93dc78-single}
\caption{QQ Plot with acceptance bands.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13878e5c92f-single}
\caption{QQ Plot rotated 45 degrees.}
\end{figure}

\section{Lineup Plot Types} \label{app:plottypes}
We can also compare participants' performance on specific types of lineup plots compared with their scores on the visual aptitude tests, for instance, accuracy on lineups which require mental rotation may be related to performance on the card rotation task.
